---
title: "Heart Failure Programme"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(leaflet)
library(sf)
library(readxl)

# Load data files
# ===============

# Load QOF Prevalence
df_qof_prev <- read.csv('D:/Data/NHSD/QOF/2023/PREVALENCE_2223.csv') %>% filter(GROUP_CODE %in% c('OB','HF'))
  
# Load QOF Achievement
df_qof_achv <- read.csv('D:/Data/NHSD/QOF/2023/ACHIEVEMENT_EAST_OF_ENGLAND_2223.csv') %>%
  bind_rows(read.csv('D:/Data/NHSD/QOF/2023/ACHIEVEMENT_LONDON_2223.csv')) %>%
  bind_rows(read.csv('D:/Data/NHSD/QOF/2023/ACHIEVEMENT_MIDLANDS_2223.csv')) %>%
  bind_rows(read.csv('D:/Data/NHSD/QOF/2023/ACHIEVEMENT_NORTH_EAST_AND_YORKSHIRE_2223.csv')) %>%
  bind_rows(read.csv('D:/Data/NHSD/QOF/2023/ACHIEVEMENT_NORTH_WEST_2223.csv')) %>%
  bind_rows(read.csv('D:/Data/NHSD/QOF/2023/ACHIEVEMENT_SOUTH_EAST_2223.csv')) %>%
  bind_rows(read.csv('D:/Data/NHSD/QOF/2023/ACHIEVEMENT_SOUTH_WEST_2223.csv')) %>%
  filter(INDICATOR_CODE == 'SMOK004' & MEASURE %in% c('NUMERATOR','DENOMINATOR','PCAS')) %>%
  select(PRACTICE_CODE, MEASURE, VALUE)
  
df_qof_achv <- df_qof_achv %>% 
  pivot_wider(names_from = 'MEASURE', values_from = 'VALUE') %>%
  mutate(DENOMINATOR = DENOMINATOR + PCAS, .keep = 'unused')

# Load QOF Organisational Mapping
df_org_map <- read.csv('D:/Data/NHSD/QOF/2023/MAPPING_NHS_GEOGRAPHIES_2223.csv')

# Load GP Registration Data
df_reg_popn <- read.csv('D:/Data/NHSD/GPREGLSOA/20240101/gp-reg-pat-prac-lsoa-all.csv') %>% 
  mutate(PRACTICE_CODE, LSOA11CD = LSOA_CODE, REG_POPN = NUMBER_OF_PATIENTS, .keep = 'none')

# Load IMD 2019 Data
df_imd19 <- read.csv('D:/Data/GOV.UK/IMD/2019/File_7_-_All_IoD2019_Scores__Ranks__Deciles_and_Population_Denominators_3.csv') %>% 
  select(1, 6) %>%
  rename_with(.fn = ~c('LSOA11CD', 'IMD_SCORE'))

# Load ePCN Data
df_pcn_members <- read_excel(path = 'D:/Data/NHSD/EPCN/20240129/ePCN.xlsx', sheet = 'PCNDetails') %>%
  select(1, 2, 3, 6, 12) %>% 
  rename_with(.fn = ~c('PCN_CODE', 'PCN_NAME', 'SUBICB', 'CLOSE_DATE', 'POSTCODE')) %>%
  filter(!is.na(CLOSE_DATE))

# Load Postcode Data
df_pcd <- read.csv('D:/Data/OpenGeography/Lookups/PCD/20231122/ONSPD_NOV_2023_UK.csv') %>% 
  select(3, 12, 13, 43, 44) %>%
  rename_with(.fn = ~c('pcds', 'easting', 'northing', 'latitude', 'longitude'))

# Load ICB Shapefile
sf_icb <- st_read(dsn = 'D:/Data/OpenGeography/Shapefiles/ICB22', layer = 'ICB22') %>%
  st_transform(crs = 4326)

# Load LSOA 2011 Shapefile
sf_lsoa11 <- st_read(dsn = 'D:/Data/OpenGeography/Shapefiles/LSOA11', layer = 'LSOA11') %>%
  st_transform(crs = 4326) %>%
  filter(grepl('^E', LSOA11CD))
```

### Chart A

***

Taken from <strong>Network-wide Cardiovascular Disease Portfolio Programme</strong> slides from the <strong>Health Innovation Network</strong>
<ul>
  <li>PCN observed baseline population prevalence + % difference to attain expected population prevalence of 1.6%</li>
  <ul>
    <li>Current population prevalence = 1.03% [QOF 22/23 data]</li>
    <li>Expected population prevalence = 1.6% - 2.0%</li>
  </ul>
</ul>
<p>References:</p>
<ul>
  <li>
https://www.ncbi.nlm.nih.gov/pmc/articles/PMC10373419/</li>
  <li>https://heart.bmj.com/content/109/7/548]</li>
</ul>
<p>Measurement: annual data capture from QOF</p>

```{r}


```

### Chart B

***

Commentary

```{r}

```

### Chart C

***

Commentary

```{r}

```

